
\section{Implementation}

\subsection{Design} 
Analyzer and the traces that are given as input. 

\subsection{Perf probe}
Describe the perf probe changes and the place that we put the probe and how it works and the data captured. 

\subsection{PIN tool design}
Describe the design of the pintool and what it does and how it does it. 

\subsection{Analysis merging}
Describe the analysis algorithm and how the merge works. This is pretty straightforward. Talk about potential loss of data.


\section{Evaluation}
We will report 3 sections here - 
\begin{itemize}
    \item The percentage of pagefaults that can be attributed to pointers for a wide variety of workloads.
    \item The performance of the vma readahead prefetcher~\cite{vma-readahead} on pointer-based pagefaults vs non-pointer based pagefaults.
\end{itemize}

Which workloads should we capture?
Smaller workloads - 
\begin{itemize}
    \item parsec.canneal 
    \item xhpcg
    \item spec 2006 from classifying paper. 
    \item workloads from hopp
\end{itemize}

Real applications - 
\begin{itemize}
    \item VoltDB
    \item Spark from canvas
    \item Redis from Dilos
    \item gapbs algorithms
    \item GraphX from HoPP
    \item Workloads from google paper
    \item workloads from tmo paper.
    \item graph mining workloads
\end{itemize}

\section{Related work}
\begin{itemize}
    \item Classifying memory access patterns for prefetching. 
    \item Angela thesis. 
\end{itemize}

\begin{itemize}
    \item Leap
    \item HoPP
    \item Canvas
    \item AiFM
    \item Fastswap
    \item others...
\end{itemize}